Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-15 ms/manuscript.Rmd
Update MS

### Climate data

We downloaded climate data at the 2.5 minute scale from the WorldClim database using the `r func("getData")` function in the R package `r pack("raster")`, and extracted four variables related to our research questions as follows: mean annual temperature (bio1; hereafter "temperature"), temperature seasonality (bio4), annual precipitation (bio12; hereafter "precipitation"), and precipitation seasonality (bio15). 
We identified the intersection of the climate data at the 2.5 minute scale with the 0.2° grid-cells, then calculated the mean of each climatic variable for each 0.2° grid-cell. 
The R package `r pack("sf")` was used for GIS analyses.

@@

Finally, a long under-appreciated aspect of fern ecology is the role of the gametophyte. 
Unlike seed plants, ferns have gametophytes that are capable of growing independently from the sporophyte. 
Futhermore, the two halves of the life cycle have vastly different morphology and ecophysiology, and may even occur over partially to completely disjunct ranges [reviewed in @Pinson2016a]. 
Here, as in the vast majority of fern ecology studies, we consider only the sporophyte phase. 
However, recent studies in Japan [@Ebihara2013; @Ebihara2019a] and elsewhere [@Nitta2017] have revealed different patterns in the distribution of gametophytes and sporophytes. 
The comprehensive molecular sampling of sporophytes in Japan makes this area ideal for conducting high-throughput DNA barcoding analyses to compare patterns of biodiversity between life cycles in ferns across large spatial scales.

>>>>

### Environmental data

We downloaded climate data at the 2.5 minute scale from the WorldClim database using the `r func("getData")` function in the R package `r pack("raster")`, and extracted four variables related to our research questions as follows: mean annual temperature (bio1; hereafter "temperature"), temperature seasonality (bio4), annual precipitation (bio12; hereafter "precipitation"), and precipitation seasonality (bio15). 
We identified the intersection of the climate data at the 2.5 minute scale with the 0.2° grid-cells, then calculated the mean of each climatic variable for each 0.2° grid-cell.
We calculated area as rolling mean area (km^2^) across 1 degree latitudinal bands.
This approach reflects the idea that the amount of area with a given climate regime enclosing each grid cell may influence species richness of that cell [@Fahrig2013], and that simply using raw island areas would not be appropriate in this context as there are just four very large islands with many much smaller ones located close by.
The R package `r pack("sf")` was used for GIS analyses.

@@

Finally, a long under-appreciated aspect of fern ecology is the role of the gametophyte. 
Unlike seed plants, ferns have gametophytes that are capable of growing independently from the sporophyte. 
Futhermore, the two stages of the life cycle have vastly different morphology and ecophysiology, and may even occur over partially to completely disjunct ranges [reviewed in @Pinson2016a]. 
Here, as in the vast majority of fern ecology studies, we consider only the sporophyte stage. 
However, recent studies in Japan [@Ebihara2013; @Ebihara2019a] and elsewhere [@Nitta2017] have revealed different patterns in the distribution of gametophytes and sporophytes. 
The comprehensive molecular sampling of sporophytes in Japan makes this area ideal for conducting high-throughput DNA barcoding analyses to compare patterns of biodiversity between life stages in ferns across large spatial scales.
